\textbf{Designing a Security Management Layer with Copy-on-Write for CDN Assets}

### 2016-03-21 tex/paper.tex
Fixed yellow comments

%}}}
\begin{abstract}
This work presents a technique for incorporating Copy-on-Write on top of an unaware persistent
storage. The system in this case is a security management system, but the technique and conclusions
drawn are general enough to be applicable to any system with vaguely similar consistency
requirements. The scalability of the storage system is tested and the technique is evaluated. The
technique is shown to be quite efficient (scalable to >6.000 simultaneous active users per node),
but a better solution is also suggested in the conclusion.\\

@@

\subsubsection{Abbreviations}
\subsubsubsection{CDN}
Content Distribution/Delivery Network - Replicates content to several servers, usually spread out
geographically. Once a request is made, the network serves content from the server closest to the
requester.

\subsubsubsection{GUID}
Global Unique Identifier - In distributed environments normal incremented identifiers can
not be used as there can be insertions on several nodes at the same time. A GUID is generated by a
function that makes it impossible or extremely unlikely that the same identifier will be generated
and used again.

\subsubsubsection{JPF}
Java Path Finder was developed by NASA and in 2005 they released it under an open source
license, which made more people contribute to the project. JPF is usually used for doing model
checking of concurrent programs to easily find for example race conditions and deadlocks.

\subsubsection{Terms}
\subsubsubsection{Eventual Consistency}
Eventual consistency is an informal guarantee that defines how the consistency of stored data can
behave. In a system defined as using eventual consistency, access to stored data is not guaranteed
to return the result of the latest modification. At some point, if modifications to the stored data
stop, access to a data item will return the resulting data of the last modification of that
item.~\cite{EVENTUAL}. It is often used in the context of database systems.

@@

A system using eventual consistency can end up in a state where there is a conflict that needs to be
handled. If for example two concurrent operations performed on two different servers changes the
same data item, a conflict of how the resulting item should look like will occur when synchronising
these servers. To solve the conflict the system needs to have a defined set of rules to be able to
determine which operation that will take precedence, or how the concurrent operations are mixed, and
this is usually called conflict or sibling resolution.

\subsubsubsection{Perius}
Perius is the name of the implementation that was made during this project. It is an anagram of
Uprise and also a type of butterfly.

\subsubsubsection{Snapshot}
A snapshot is a way to record the full state of a system at a specific time. The term comes from
photography where a photo can be seen as the state of what the photo is of, at a certain time.
Snapshots should not be confused with a full copy of a system, or part of a system, as full copies 
can be used as backups meanwhile snapshots are not very effective means of backup in the case of 
data corruption. It is not effective against data corruption as snapshots usually still refer to 
unchanged data that is still a part of the system~\cite{SNAPSHOT}.

\newpage
\section{Model} \label{sec:model}
The model for this work should show how the data can only be accessed or modified by authorized
users and how the defined integrity of the data is always kept in the Perius system.

@@

\par \textbf{Content} \\
Content is metadata about a file and is stored in a container, it is a form of virtual file.  The
content can refer to for example an image, video or binary blob.\\

>>>>

%}}}
\begin{abstract}
This work presents a technique for implementing Copy-on-Write on top of an unaware persistent
storage. The system in this case is a security management system, but the technique and conclusions
drawn are general enough to be applicable to any system with vaguely similar consistency
requirements. The scalability of the storage system is tested and the technique is evaluated. The
technique is shown to be quite efficient (scalable to >6.000 simultaneous active users per node),
but a better solution is also suggested in the conclusion.\\

@@

\subsubsection{Abbreviations}
\begin{description}

\item[CDN] \hfill \\
Content Distribution/Delivery Network - Replicates content to several servers, usually spread out
geographically. Once a request is made, the network serves content from the server closest to the
requester.

\item[GUID] \hfill \\
Global Unique Identifier - In distributed environments normal incremented identifiers can
not be used as there can be insertions on several nodes at the same time. A GUID is generated by a
function that makes it impossible or extremely unlikely that the same identifier will be generated
and used again.

\item[JPF] \hfill \\
Java Path Finder was developed by NASA and in 2005 they released it under an open source
license, which made more people contribute to the project. JPF is usually used for doing model
checking of concurrent programs to easily find for example race conditions and deadlocks.

\end{description}

\subsubsection{Terms}
\begin{description}
\item[Eventual Consistency] \hfill \\
Eventual consistency is an informal guarantee that defines how the consistency of stored data can
behave. In a system defined as using eventual consistency, access to stored data is not guaranteed
to return the result of the latest modification. At some point, if modifications to the stored data
stop, access to a data item will return the resulting data of the last modification of that
item.~\cite{EVENTUAL}. It is often used in the context of database systems.

@@

A system using eventual consistency can end up in a state where there is a conflict that needs to be
handled. If for example two concurrent operations performed on two different servers changes the
same data item, a conflict of how the resulting item should look like will occur when synchronising
these servers. To solve the conflict the system needs to have a defined set of rules to be able to
determine which operation that will take precedence, or how the concurrent operations are mixed,
which is usually called conflict or sibling resolution. %% Clock sync and check time as rule

\item[Perius] \hfill \\
Perius is the name of the implementation that was made during this project. It is an anagram of
Uprise and also a type of butterfly.

\item[Snapshot] \hfill \\
A snapshot is a way to record the full state of a system at a specific time. The term comes from
photography where a photo can be seen as the state of what the photo is of, at a certain time.
Snapshots should not be confused with a full copy of a system, or part of a system, as full copies
can be used as backups meanwhile snapshots are not very effective means of backup in the case of
data corruption. Snapshots are not effective against data corruption as snapshots usually still
refer to unchanged data that is still a part of the system~\cite{SNAPSHOT}.

\end{description}
\newpage
\section{Model} \label{sec:model}
The model for this work shows how the data can only be accessed or modified by authorized
users and how the defined integrity of the data is always kept in the Perius system.

@@

\hfill \par \textbf{Content} \\
Content is metadata about a file and is stored in a container, it is a form of virtual file.  The
content can refer to for example an image, video or binary blob.\\
